Empirical Study of Scientific Computer Software: Objectives and Research Questions

### 2020-06-02 OverallResearchProposal/ObjectivesAndResearchQuestions.tex
Minor notes added to quality definition document related to reproducibility

\textbf{What knowledge needs to be captured and what principles, processes and
  methodologies followed to produce sustainable \{software + artifacts\} with
  a reasonable amount of time and energy?}\\

In the above definition, software is considered to be an application (app)
and/or a library.  The outcome of the development process is not just software.
It is \{software + artifacts\}.  From this point onward, we will use the term
softifacts when we are referencing the combination of software and the
associated artifacts.  The artifacts consist of such work products as
documentation, build scripts, code, test cases, contributor's guides, etc.  The
quality of sustainability cannot be assessed by looking at the software alone,
or the code alone; it depends on everything, including the processes and
methodologies used during the development.  Further information on the relevant
definitions and context is given in the next section.

@@

In the statement of the objective, principles, processes and methodologies are
listed, but not tools.  Tools are needed to support methodologies, but tools
change rapidly.  Our goal is to be more general.  If the right principles,
processes and methodologies are found, the tools will adapt to match.  However,
understanding the current state of the practice will involve looking at tools,
as shown in the later list of research questions.

@@

  This definition is general; it is not specific to software and it is silent on
  the specific needs of the present and the future.  The definition can be made
  less abstract by introducing the context of softifacts and thinking
  separately about the needs of the present and the future.  For the needs of
  the present, the software should be correct, reliable and usable. For the
  needs of the future, given uncertainty, this means supporting change from
  relevant concerns (political, economic, social, technical, legal and
  environmental) should be possible with a reasonable level of resources.
  Supporting the future then means producing softifacts that are
  maintainable, portable, reusable and reproducible.

>>>>

OLD \textbf{What is needed knowledge needs to be captured and what principles, processes and
  methodologies followed to produce sustainable \{software + artifacts\} with
  a reasonable amount of time and energy?}\\

\textbf{What is needed to produce sustainable \{software + artifacts\}?}\\

Define software.

Define sustainable.  We start with the general definition:

Might be better to use the adopted definition - since it uses qualities, which
are terms that we need.

Define softifacts.  In the above definition, software is considered to be an application (app)
and/or a library.  The outcome of the development process is not just software.
It is \{software + artifacts\}.  From this point onward, we will use the term
softifacts when we are referencing the combination of software and the
associated artifacts.  The artifacts consist of such work products as
documentation, build scripts, code, test cases, contributor's guides, etc.  The
quality of sustainability cannot be assessed by looking at the software alone,
or the code alone; it depends on everything, including the processes and
methodologies used during the development.  Further information on the relevant
definitions and context is given in the next section.

What is needed - In the statement of the objective, principles, processes and
methodologies are listed, but not tools.  Tools are needed to support
methodologies, but tools change rapidly.  Our goal is to be more general.  If
the right principles, processes and methodologies are found, the tools will
adapt to match.  However, understanding the current state of the practice will
involve looking at tools, as shown in the later list of research questions.

@@

@@

  This definition is general; it is not specific to software and it is silent on
  the specific needs of the present and the future.  The definition can be made
  less abstract by introducing the context of softifacts and thinking
  separately about the needs of the present and the future.  For the needs of
  the present, the software should meet its requirements specification.
  \wss{highlight correctness? reliability?}  For the
  needs of the future, given uncertainty, this means supporting change from
  relevant concerns (political, economic, social, technical, legal and
  environmental) should be possible with a reasonable level of resources.
  Supporting the future then means producing softifacts that are
  maintainable, reusable and reproducible.
